---
title: "Your Paper Title Here"
author: "Your Name(s)"
date: Date
output: pdf_document
urlcolor: blue
header-includes:
- \usepackage{amsmath,amsfonts,amssymb}
- \usepackage{setspace} \doublespacing
fontsize: 11pt
---

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
```

# Abstract
Write your abstract here.

# Keywords
*Keyword 1*, *Keyword 2*, *Keyword 3*, *Keyword 4*

\newpage

# Introduction / Background
Provide an introduction with background information.

```{r label="important_R_code", eval=TRUE, echo=FALSE}
df <- data.frame(
  Group= c("BNT162b2", "Placebo", "Total"),
  Infected= c(8, 162, 170),
  Uninfected=c(17403,17349,34752),
  Sample_size= c(17411, 17511, 34922)
)
kable(df, caption = "Vaccine Efficacy in Trails ")
```

```{r label="important_R_code", eval=TRUE, echo=FALSE}
df$InfectionRate <- 100 * df$Infected / df$Sample_size
df
df_no_total <- subset(df, Group != "Total")
ggplot(df_no_total, aes(x = Group, y = InfectionRate)) +
  geom_bar(stat = "identity", fill = "steelblue", width = 0.4) +
  geom_text(aes(label = paste0(round(InfectionRate, 5), "%")), 
            vjust = -0.5, 
            size = 4) +
  labs(
    title = "Infection Rate by Group",
    x = "Group",
    y = "Infection Rate (%)"
  ) +
  theme_minimal()
```

```{r label="important_R_code", eval=TRUE, echo=FALSE}
groups <- c("BNT162b2", "Placebo")
infected <- c(8, 162)
pie(
  x = infected,
  labels = groups,
  main = "Infected Cases by Group"
)
```
# Statistical Methods

## Model
Describe the statistical model used.

## Likelihood Inference
Detail the likelihood approach.

## Bayesian Inference
Detail the Bayesian approach.

# Results
Present your findings. 

# Discussion / Conclusion
Discuss / conclude here.

# Bibliography

Brown, B. (2024). *Lecture Title*. Lecture slides, Course Name, University Name.

Doe, J. (2020). Title of the Paper. *Journal Name*, 12(3), 45-67.

Last, F., & Last, F. (2025). *Book Title*. Publisher.

Smith, A., & Johnson, C. (2023). *Title of the Online Article*. Retrieved from https://www.example.com.

# Appendix

## Code
```{r ref.label = "important_R_code", eval=FALSE}
```

## Proofs
If applicable, include detailed mathematical derivations or additional theoretical explanations.
