---
title: "Your Paper Title Here"
author: "Your Name(s)"
date: Date
output: pdf_document
urlcolor: blue
header-includes:
- \usepackage{amsmath,amsfonts,amssymb}
- \usepackage{setspace} \doublespacing
fontsize: 11pt
---

```{r setup, include=FALSE}
library(ggplot2)
```

# Abstract
Write your abstract here.

# Keywords
*Keyword 1*, *Keyword 2*, *Keyword 3*, *Keyword 4*

\newpage

# Introduction / Background
Provide an introduction with background information.

## Dataframe: 
```{r label="important_R_code", eval=TRUE, echo=FALSE}
df <- data.frame(
  Group= c("BNT162b2", "Placebo", "Total"),
  Infected= c(8, 162, 170),
  Uninfected=c(17403,17349,34752),
  Sample_size= c(17411, 17511, 34922)
)
```

## Data Visualization (bar-chart)
```{r label="important_R_code", eval=TRUE, echo=FALSE}
df$InfectionRate <- 100 * df$Infected / df$Sample_size
df
df_no_total <- subset(df, Group != "Total")
ggplot(df_no_total, aes(x = Group, y = InfectionRate)) +
  geom_bar(stat = "identity", fill = "steelblue", width = 0.4) +
  geom_text(aes(label = paste0(round(InfectionRate, 5), "%")), 
            vjust = -0.5, 
            size = 4) +
  labs(
    title = "Infection Rate by Group",
    x = "Group",
    y = "Infection Rate (%)"
  ) +
  theme_minimal()
```

## Data Visualization (pie chart)
```{r label="important_R_code", eval=TRUE, echo=FALSE}
groups <- c("BNT162b2", "Placebo")
infected <- c(8, 162)
pie(
  x = infected,
  labels = groups,
  main = "Infected Cases by Group"
)
```

## Summary:
```{r}
pi_b_hat <- 8 / 17411
pi_p_hat <- 162 / 17511
```
$\hat{\pi}_b =$ `r pi_b_hat`, where $\hat{\pi}_b$ is the estimated probability that people who take the vaccine will be infected by COVID-19. 
$\hat{\pi}_p =$ `r pi_p_hat`, where $\hat{\pi}_p$ is the estimated probability that people who didn't take the vaccine will be infected by COVID-19.

Therefore, the vaccine efficacy $\psi$ is 
$$
\psi = \frac{\hat{\pi}_p - \hat{\pi}_b}{\hat{\pi}_p} \approx 0.95
$$

```{r}
psi <- (pi_p_hat - pi_b_hat) / pi_p_hat
psi
```



# Statistical Methods

## Defining the Random Variables and Statistical Model
Let us denote $X_v$ = the number of laboratory-confirmed COVID-19 cases
in the vaccine (BNT162b2) group and $X_p$ = the number of cases in the
placebo group. We assume that
$$
X_v \sim \mathrm{Binomial}(n_v, p_v),
$$ 
where $n_v = 17{,}411$ is the number of subjects in the vaccine arm
and $p_v$ is the (unknown) probability of infection in the vaccine
group. Similarly, 
$$
X_p \sim \mathrm{Binomial}(n_p, p_p),
$$ 
where $n_p = 17{,}511$ is the number of subjects in the placebo arm
and $p_p$ is the (unknown) probability of infection in the placebo
group.

## Approaches to Data Analysis

We employ two different approaches to analyze the data: a Bayesian
approach and a likelihood-based (frequentist) approach. Each approach is
detailed below.

## Parameters and Hypotheses

The parameters of interest are:

```{=tex}
\begin{itemize}
    \item $p_v$ and $p_p$: the infection probabilities in the vaccine and placebo groups.
    \item $f_i$: the transformed parameter defined as above, from which vaccine efficacy 
    is derived by $\mathrm{VE} = 1 - f_i$.
\end{itemize}
```
The primary hypothesis of interest is to assess the efficacy of the
vaccine. Specifically, we wish to test whether the vaccine efficacy
exceeds a clinically meaningful threshold. For example, one might
formalize the hypothesis as: \begin{align*}
H_0 &: \mathrm{VE} \le 30\%, \\
H_a &: \mathrm{VE} > 30\%.
\end{align*}

In the Pfizer analysis, the posterior probability
$\Pr(\mathrm{VE} > 30\%)$ was found to be larger than 0.9999.


## Model
Describe the statistical model used.

## Likelihood Inference
Detail the likelihood approach.

## Bayesian Inference
Detail the Bayesian approach.

\subsection{Vaccine Efficacy Definition}

The vaccine efficacy (VE) is defined via the transformation $$
\mathrm{VE} = 1 - \frac{p_v}{p_v + p_p},
$$ so that we may introduce the parameter $$
f_i = \frac{p_v}{p_v + p_p},
$$ and thus, $\mathrm{VE} = 1 - f_i$. In the study by Polack et al., the
prior for $f_i$ was specified as $$
f_i \sim \mathrm{Beta}(0.700102,\,1),
$$ reflecting the belief (with a six-decimal precision) about the
infection probability ratio.
which means that the BNT162b2 vaccine reduces the risk of COVID-19 infection by about 95% relative to those who did not receive the vaccine. 
# Results
Present your findings. 

# Discussion / Conclusion
Discuss / conclude here.

# Bibliography

Brown, B. (2024). *Lecture Title*. Lecture slides, Course Name, University Name.

Doe, J. (2020). Title of the Paper. *Journal Name*, 12(3), 45-67.

Last, F., & Last, F. (2025). *Book Title*. Publisher.

Smith, A., & Johnson, C. (2023). *Title of the Online Article*. Retrieved from https://www.example.com.

# Appendix

## Code
```{r ref.label = "important_R_code", eval=FALSE}
```

## Proofs
If applicable, include detailed mathematical derivations or additional theoretical explanations.
